Exp1 - Opt w_max and {A,phi)

### 2018-03-12 voltagebudget/analysis/paper_figures.Rmd
Tweaks to paper figs

```{r, fig.width=1.7, fig.height=1.8}
fig2 %>% 
  filter(freq == 20) %>% 
  ggplot(aes(x=errors*1e3, y=variances*1e3, color=V_osc*1e3)) +
  geom_point(size=0.05, alpha=.1) +
  scale_color_gradient(low="purple", high="red", name=expression(V[o] (mvolt))) +
  labs(x="Error (ms)", y="Variance (ms)") +
  theme_classic() +
  theme(
    legend.position="bottom", 
    legend.key.size = unit(.5, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8)) -> p1

@@

plot_grid <- rbind(
  c(NA, NA, NA, 4, 4,   4),
  c(NA, NA, NA, 4, 4,   4),
  c(NA, NA, NA, 2, 2,   2),
  c(1,  1,  1,  2, 2,   2),
  c(1,  1,  1,  3, 3,   3),
  c(1,  1,  1,  3, 3,   3),
  c(1,  1,  1,  NA, NA, NA))
grid.arrange(p1, p2, p3, p4, layout_matrix=plot_grid)
rm(p1, p2, p3, plot_grid)
```

@@

fig1 %>% 
  filter(freq == 20) %>% 
  ggplot(aes(x=V_osc*1e3, y=variances*1e3)) +
  geom_point(size=0.1, alpha=0.1, color="grey") + 
  theme_classic() +
  geom_line(data=filter(fig2, freq==20), 
            aes(x=V_osc*1e3, y=variances*1e3), 
            color="black", size=0.7, alpha=1) +
  labs(x=expression(V[o] (mvolt)), y="Variance (ms)") -> p1

fig1 %>% 
  filter(freq==20) %>% 
  filter(V_osc/V_comp <= 3) %>% 
  filter(N %in% sample(1:max_N, 10, replace = FALSE)) %>% 
  ggplot(aes(x=V_osc*1e3, y=variances*1e3, color=factor(delta_spikes))) +
  geom_point(size=1, alpha=1) + 
  facet_wrap(~rank, ncol=2) +
  geom_line(data=filter(fig2, freq==20), 
            aes(x=V_osc*1e3, y=variances*1e3), 
            color="black", size=0.7, alpha=1) +
  scale_colour_brewer(palette = "Accent", name="N spikes") +
  scale_x_continuous(breaks=c(0, 3, 6)) +
  scale_y_continuous(breaks=c(6, 8)) +
  labs(x=expression(V[o] (mvolt)), y="Variance (ms)") +
  theme_classic() + theme(
    # legend.position="bottom",
    strip.text.x = element_text(size=0),
    strip.background = element_blank(),
    legend.position="none", 
    legend.key.size = unit(.5, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8),
    # axis.line=element_blank(),
    # axis.text.x=element_blank(),
    # axis.text.y=element_blank(),
    # axis.ticks=element_blank(),
    # axis.title.x=element_blank(),
    # axis.title.y=element_blank(),
    panel.background=element_blank(),
    # panel.border=element_blank(),
    # panel.grid.major=element_blank(),
    # panel.grid.minor=element_blank(),
    plot.background=element_blank()) -> p2

fig1 %>% 
  filter(freq==20) %>% 
  filter(V_osc/V_comp <= 3) %>% 
  filter(N %in% sample(1:max_N, 5, replace = FALSE)) %>% 
  ggplot(aes(x=V_osc*1e3, y=errors*1e3, color=factor(delta_spikes))) +
  geom_point(size=1, alpha=1) + 
  facet_wrap(~rank, ncol=1) +
  geom_line(data=filter(fig2, freq==20), 
            aes(x=V_osc*1e3, y=errors*1e3), 
            color="black", size=0.7, alpha=1) +
  scale_colour_brewer(palette = "Accent", name="N spikes") +
  scale_x_continuous(breaks=c(0, 3, 6)) +
  scale_y_continuous(breaks=c(2, 8)) +
  labs(x=expression(V[o] (mvolt)), y="Error (ms)") +
  theme_classic() + theme(
    # legend.position="bottom",
    strip.text.x = element_text(size=0),
    strip.background = element_blank(),
    legend.position="right", 
    legend.key.size = unit(.5, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8),
    # axis.line=element_blank(),
    # axis.text.x=element_blank(),
    # axis.text.y=element_blank(),
    # axis.ticks=element_blank(),
    # axis.title.x=element_blank(),
    # axis.title.y=element_blank(),
    panel.background=element_blank(),
    # panel.border=element_blank(),
    # panel.grid.major=element_blank(),
    # panel.grid.minor=element_blank(),
    plot.background=element_blank()) -> p3

>>>>

```{r, fig.width=1.9, fig.height=1.8}
fig2 %>% 
  filter(freq == 20) %>% 
  ggplot(aes(x=errors*1e3, y=variances*1e3, color=V_osc*1e3)) +
  geom_point(size=0.05, alpha=.1) +
  scale_color_gradient(low="purple", high="red", name=expression(V[o] (mvolt))) +
  labs(x="Error (ms)", y="Variance (ms)") +
  theme_classic() +
  theme(
    legend.position="bottom", 
    legend.key.size = unit(.4, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8)) -> p1

@@

plot_grid <- rbind(
  c(NA, NA, NA, 4, 4,   4),
  c(NA, NA, NA, 4, 4,   4),
  c(1, 1, 1, 2, 2,   2),
  c(1,  1,  1,  2, 2,   2),
  c(1,  1,  1,  3, 3,   3),
  c(1,  1,  1,  3, 3,   3))#,
  # c(1,  1,  1,  NA, NA, NA))
grid.arrange(p1, p2, p3, p4, layout_matrix=plot_grid)
rm(p1, p2, p3, plot_grid)
```

@@

fig1 %>% 
  filter(freq == 20) %>% 
  ggplot(aes(x=V_osc*1e3, y=variances*1e3)) +
  geom_point(size=0.1, alpha=0.1, color="grey") + 
  theme_classic() +
  geom_line(aes(x=V_osc*1e3, y=variances_pop*1e3), 
            color="black", size=0.7, alpha=1) +
  labs(x=expression(V[o] (mvolt)), y="Variance (ms)") -> p1

fig1 %>% 
  filter(freq==20) %>% 
  filter(V_osc/V_comp <= 3) %>% 
  filter(N %in% sample(1:max_N, 10, replace = FALSE)) %>% 
  ggplot(aes(x=V_osc*1e3, y=variances*1e3, color=factor(delta_spikes))) +
  geom_point(size=1, alpha=1) + 
  facet_wrap(~rank, ncol=2) +
  geom_line(aes(x=V_osc*1e3, y=variances_pop*1e3), 
            color="black", size=0.7, alpha=1) +
  scale_colour_brewer(palette = "Accent", name="N spikes") +
  scale_x_continuous(breaks=c(0, 3, 6)) +
  scale_y_continuous(breaks=c(6, 8)) +
  labs(x=expression(V[o] (mvolt)), y="Variance (ms)") +
  theme_classic() + theme(
    # legend.position="bottom",
    strip.text.x = element_text(size=0),
    strip.background = element_blank(),
    legend.position="none", 
    legend.key.size = unit(.5, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8),
    # axis.line=element_blank(),
    # axis.text.x=element_blank(),
    # axis.text.y=element_blank(),
    # axis.ticks=element_blank(),
    # axis.title.x=element_blank(),
    # axis.title.y=element_blank(),
    panel.background=element_blank(),
    # panel.border=element_blank(),
    # panel.grid.major=element_blank(),
    # panel.grid.minor=element_blank(),
    plot.background=element_blank()) -> p2

fig1 %>% 
  filter(freq==20) %>% 
  filter(V_osc/V_comp <= 3) %>% 
  filter(N %in% sample(1:max_N, 5, replace = FALSE)) %>% 
  ggplot(aes(x=V_osc*1e3, y=errors*1e3, color=factor(delta_spikes))) +
  geom_point(size=1, alpha=1) + 
  facet_wrap(~rank, ncol=1) +
  geom_line(aes(x=V_osc*1e3, y=errors_pop*1e3), 
            color="black", size=0.7, alpha=1) +
  scale_colour_brewer(palette = "Accent", name="N spikes") +
  scale_x_continuous(breaks=c(0, 3, 6)) +
  scale_y_continuous(breaks=c(2, 8)) +
  labs(x=expression(V[o] (mvolt)), y="Error (ms)") +
  theme_classic() + theme(
    # legend.position="bottom",
    strip.text.x = element_text(size=0),
    strip.background = element_blank(),
    legend.position="right", 
    legend.key.size = unit(.5, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8),
    # axis.line=element_blank(),
    # axis.text.x=element_blank(),
    # axis.text.y=element_blank(),
    # axis.ticks=element_blank(),
    # axis.title.x=element_blank(),
    # axis.title.y=element_blank(),
    panel.background=element_blank(),
    # panel.border=element_blank(),
    # panel.grid.major=element_blank(),
    # panel.grid.minor=element_blank(),
    plot.background=element_blank()) -> p3
